---
title: 'Asian Development Bank DEMO'
author: 'Krashaldy Muñoz'
date: 'December 6, 2018'
output: html_document
---

#Investor Statistics Panel Charts

This document contains all of the charts and data used to create the wireframe for the Investment Dashboard for the proposed InfraNav Statistics Panel.

First I need to define the list of countries that will be used for this analysis.

They can be seperated in to two regions

* South Asia
    + Bangladesh
    + Pakistan
    + Sri Lanka
    
* Southeast Asia
    + Indonesia
    + Vietnam
    + Thailand
    + Malaysia
    + Philippines
    + Cambodia
    
Country     | iso Code
----------- | ------------
Bangladesh  | BGD
Pakistan    | PAK 
Sri Lanka   | LKA
Indonesia   | IDN
Vietnam     | VNM
Thailand    | THA
Malaysia    | MYS
Philippines | PHL
Cambodia    | KHM
***

## Required Packages

```{r message=FALSE}
#Load Required Packages
library(openxlsx)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(magrittr)
library(wbstats)
```
***
## Data Importation

This is Data for the Regional Branch (International)

```{r message=FALSE}
#Country Selection

countries <- c('Bangladesh', 'Pakistan', 'Sri Lanka', 'Indonesia', 'Vietnam', 'Thailand', 'Malaysia', 'Philippines', 'Cambodia')

countries_iso <- c('BGD', 'PAK', 'LKA', 'IDN', 'VNM', 'THA', 'MYS', 'PHL', 'KHM')

#Table Creation

asiaFibreach <- read.xlsx('findex-data/Asia_fibreach_dec2018.xlsx', 1)
  
asiaRoW <- read.xlsx('findex-data/Asia_RoW.xlsx', 1)
  
asiaNetworks <- read.xlsx('findex-data/networks.xlsx', 2)

asiaProviders <- read.csv('findex-data/provider_metrics.csv')
  
populatedPlaces <- read.csv('findex-data/populated_places.csv')

wbData <- wb(country = countries_iso,
             indicator = c('IT.NET.BBND.P2', 'IT.CEL.SETS.P2', 'SP.POP.TOTL', 'SP.RUR.TOTL.ZS', 'SP.DYN.IMRT.IN', 'SP.DYN.LE00.IN'),
             mrv = 7)

finBase <- read.xlsx('findex-data/globalFindexdatabase.xlsx', 1)

asiaSpectrum <- read.csv('findex-data/spectrum_merged_csv.csv')
```

This is data for the Subnational Perspective (Bangladesh)

```{r message=FALSE}
bgdHospCt <- read.csv('findex-data/bangladesh - hospital ct.csv')

bgdHospR <- read.csv('findex-data/bgd_hosp_within5km.csv')

bgdAdm3 <- read.xlsx('findex-data/bgd_adm3.xlsx',1)

bgdFinReach <- read.xlsx('findex-data/bgd_fin_reach.xlsx',1)
```
***
## Data Cleaning

### Selected Asian Countries

```{r echo=FALSE}
summary(wbData)
```

#### Regional Donut Chart

```{r echo=FALSE}
asiaPopulation <- wbData %>% filter(indicator == 'SP.POP.TOTL')
fiberdata <- asiaFibreach
fiberdata <- merge(fiberdata, asiaPopulation, by.x = 'ctry', by.y = 'iso3c', all = TRUE)
fiberdata <- dplyr::select(fiberdata, country, `5.km.reach`, value)
fiberdata <- fiberdata[-c(3,6,7,11,13),]
fiberdata <- data.frame(region = 'asia', reach = sum(fiberdata$`5.km.reach`), pop = sum(fiberdata$value)) 
fiberdata <- dplyr::mutate(fiberdata, 'reach.%' = (reach/pop)*100)
fiberdata

asiaDonut <- data.frame(count=c(41.62, 58.38), category=c('A', 'B'))
asiaDonut$fraction = asiaDonut$count / sum(asiaDonut$count)
asiaDonut = asiaDonut[order(asiaDonut$fraction), ]
asiaDonut$ymax = cumsum(asiaDonut$fraction)
asiaDonut$ymin = c(0, head(asiaDonut$ymax, n=-1))

p1 <- ggplot(asiaDonut, aes(fill=category, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) + 
  geom_rect(colour="grey30") + 
  coord_polar(theta="y") + 
  xlim(c(0, 4)) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  theme(axis.text=element_blank()) +
  theme(axis.ticks=element_blank()) +
  scale_fill_manual(values = c('#e0e0e0','#0D6EB8')) +
  labs(title="South Asia: Fiber Reach (%)")
p1
```


#### Fiber Reach by Country

```{r echo=FALSE}
fiberdata <- asiaFibreach
asiaPopulation <- wbstats::wb(country = c('BGD', 'PAK', 'LKA', 'IDN', 'VNM', 'THA', 'MYS', 
                                          'PHL', 'KHM'), 
                             indicator = 'SP.POP.TOTL', mrv = 1)
fiberdata <- merge(fiberdata, asiaPopulation, by.x = 'ctry', by.y = 'iso3c', all = TRUE)
fiberdata <- dplyr::select(fiberdata, country, `5.km.reach`, value)
fiberdata <- dplyr::mutate(fiberdata, reach_perc = (`5.km.reach`/ value)*100) 
fiberdata <- fiberdata[-c(3,6,7,11,13),]

fiberchart <- ggplot(fiberdata, aes(x=reorder(country, dplyr::desc(country)), y=reach_perc)) +
  geom_col(aes(fill=country)) +
  theme(legend.position = 0) +
  coord_flip() +
  geom_hline(yintercept=58.38, color='#0D6EB8', size=1.5) +
  labs(x='Country', y='5km Fiber Reach (% of the Population)')
fiberchart
```


#### Spectrum 

```{r echo=FALSE}
asiaSpectrum <- asiaSpectrum %>% 
  filter(country %in% countries) %>% 
  select(country, iso_a3, provider, band_mhz, pairs, allocation, technology, year, src_band, src_pairs)

summary(asiaSpectrum)
```


### Bangladesh

#### Hospital Count by Administrative Layer (bgdHospCt)

```{r}
#Remove Irrelevant Columns
bgdHospCt <- bgdHospCt[,c(3:10)]

#Subset Data for Adm1
bgdHospCt1 <- bgdHospCt %>% 
  group_by(name_1) %>% 
  summarise(pop = sum(pop, na.rm = TRUE),
            area = sum(area, na.rm = TRUE),
            hosp = sum(hosp_ct, na.rm = TRUE)) %>% 
  mutate(popden = pop/area)

#Subset Data for Adm2
bgdHospCt2 <- bgdHospCt %>% 
  group_by(name_2) %>% 
  summarise(pop = sum(pop, na.rm = TRUE),
            area = sum(area, na.rm = TRUE),
            hosp = sum(hosp_ct, na.rm = TRUE)) %>% 
  mutate(popden = pop/area) 

#More Granular Table
bgdHospCt3 <- bgdHospCt[,c(3,2)]
bgdHospCt3 <- distinct(bgdHospCt3, name_2, .keep_all = TRUE)
bgdHospCt3 <- merge(bgdHospCt2, bgdHospCt3, by.x='name_2', by.y='name_2', all.x=TRUE)


summary(bgdHospCt2)
str(bgdHospCt2)

b1 <- ggplot(bgdHospCt1, aes(name_1, hosp)) +
  geom_col()
b1

b2 <- ggplot(bgdHospCt3, aes(popden, hosp)) +
  geom_point(aes(color=name_1), size=2)
b2 

b3 <- ggplot(bgdHospCt3, aes(name_1, hosp)) +
  geom_point(aes(color=name_1), size=2)
b3

b4 <- ggplot(bgdHospCt3, aes(name_1, popden)) +
  geom_point(aes(color=name_1), size=2)
b4
```


#### Hospitals within 5km of Fiber (bgdHospR)

```{r fig.height=4, fig.width=8}
#Remove Irrelevant Columns

bDiv1 <- c('Barisal', 'Chittagong', 'Dhaka', 'Khulna', 'Mymensignh', 'Rajshahi', 'Rangpur', 'Sylhet')

bgdHospR <- bgdHospR[,c(7,8,18,20,21)]

bgdHospR1 <- bgdHospR %>% 
  filter(within_5km == TRUE, adm1_name %in% bDiv1) %>% 
  group_by(adm1_name) %>% 
  summarise(hosp_ct = n()) %>% 
  mutate(within_5km = TRUE)

bgdHospR2 <- bgdHospR %>% 
  filter(within_5km == FALSE, adm1_name %in% bDiv1) %>% 
  group_by(adm1_name) %>% 
  summarise(hosp_ct = n()) %>% 
  mutate(within_5km = FALSE)

bgdHospR3 <- merge(bgdHospR1, bgdHospR2, by.x='adm1_name', by.y='adm1_name', all.x=TRUE)
bgdHospR3 <- bind_rows(bgdHospR1, bgdHospR2)
bgdHospR3 

b5 <- ggplot(bgdHospR3, aes(adm1_name, hosp_ct)) +
  geom_col(aes(fill=within_5km))
b5

```


#### bgdAdm3

```{r}
#Remove Irrelevant Columns
bgdAdm3 <- bgdAdm3[,-c(1,2,14)]

summary(bgdAdm3)
str(bgdAdm3)
```


#### Population within 1km of a bank and/or Mobile Money Agent (bgdFinReach)

```{r fig.height=3, fig.width=6}
bgdFinReach <- mutate(bgdFinReach,
                      perc_bank = (pop.with.1km.of.bank/total.pop)*100,
                      perc_mma = (pop.with.1km.of.a.mobile.money.agent/total.pop)*100,
                      no_access= 100 - (perc_bank + perc_mma))
bgdFinReach <- bgdFinReach %>% gather(type, value, 5:7) %>% select(adm1_name, type, value)

bfinal <- ggplot(bgdFinReach, aes(reorder(adm1_name, desc(adm1_name)), value))+
  geom_col(aes(fill=type)) +
  coord_flip() +
  labs(x = 'Country', y='% of Population') +
  scale_y_continuous(limits = c(0,100), expand = c(0,0))
bfinal
#bgdFinReach
```

