---
title: 'Regulator Dashboard Charts'
author: 'Krashaldy Muñoz'
date: 'December 12, 2018'
output: html_document
---
### Overview

This Dashboard will be divded into 2 main views, Subnatinional and National(with the former coming in first). Regulators will be more interested in subnational Data. A compliance tab might be included in the dashboard at a later date, or it might be a complete separate "view" from the others.

***
#### Packages

```{r message=FALSE}
library(openxlsx)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(magrittr)
library(wbstats)
library(ggrepel)
library(wesanderson)
```

#### Countries

```{r message=FALSE}
countries <- c('Bangladesh', 'Pakistan', 'Sri Lanka', 'Indonesia', 'Vietnam', 'Thailand', 'Malaysia', 'Philippines', 'Cambodia')

countries_iso <- c('BGD', 'PAK', 'LKA', 'IDN', 'VNM', 'THA', 'MYS', 'PHL', 'KHM')
```


### Subnational: Fiber

#### Load Data

```{r message=FALSE}
bgdPopulated <- read.csv("findex-data/populated_places.csv") %>% 
  filter(iso_a3 == "BGD") %>% 
  select(country, iso_a3, name, type, population, src_pop, pop_src_yr, within_5km, adm1_name, fib_dist, pop_perc) %>% 
  group_by(adm1_name) %>% 
  summarise(population = sum(population, na.rm = TRUE),
            fib_dist = sum(fib_dist, na.rm = TRUE)) %>% 
  subset(adm1_name %in% c("Barisal", "Chittagong", "Dhaka", "Khulna", "Rajshahi", "Rangpur", "Sylhet")) %>% 
  mutate(reach = (fib_dist/population)*100)
```

#### Chart

```{r echo=FALSE}
bgdPopulated
```

### Subnational: Rights of Way

#### Load Data

```{r message=FALSE}
asiaRoW <- read.xlsx("findex-data/Asia_RoW.xlsx", 1) %>% 
  filter(Country %in% countries)
```

#### Chart

```{r echo=FALSE}
asiaRoW
```

### Subnational: Spectrum

#### Load Data

```{r message=FALSE}
spectrumData <- read.csv("findex-data/spectrum_merged_csv.csv") %>% 
  filter(iso_a3 %in% countries_iso) %>% 
  select(country, iso_a3, provider, band_mhz)
```

#### Chart

```{r echo=FALSE}
summary(spectrumData)
str(spectrumData)
```


***

### National: Fiber

#### Load Data

```{r message=FALSE}
asiaFiber <- read.xlsx("findex-data/Asia_fibreach_dec2018.xlsx", 1) %>% 
  filter(ctry %in% countries_iso)

asiaPopulation <- wb(country = countries_iso, indicator = c('SP.POP.TOTL'), mrv = 1) %>% 
  select(iso3c, value) %>% 
  rename(ctry = 'iso3c', pop = 'value')

asiaReach <- left_join(asiaFiber, asiaPopulation, by="ctry", all=TRUE) %>% 
  mutate(reach = (`5.km.reach`/pop)*100)

asiaNet <- read.xlsx("findex-data/networks.xlsx", 1) %>% 
  filter(iso_a3 %in% countries_iso, `fiber?` == "yes") %>% 
  select(iso_a3, provider.name, `fiber?`, longhaul.km, metro.km, access.km, leased.km, distinct.km.total, indistinct.km.total )
```

#### Charts

```{r echo=FALSE}
asiaReach
#asiaNet
fiberchart <- ggplot(asiaReach, aes(x=reorder(ctry, dplyr::desc(ctry)), y=reach)) +
  geom_col(aes(fill=ctry)) +
  coord_flip() +
  geom_hline(yintercept=58.38, color='#0D6EB8', size=1.5) +
  labs(x='Country', y='5km Fiber Reach (% of the Population)') +
  scale_y_continuous(limits = c(0,90), expand = c(0,0), breaks = c(0,20,40,60,80)) +
  theme_bw() + scale_fill_brewer(palette="Set1") +
  theme(legend.position = 0)
fiberchart
```

### National: Rights of Way

#### Load Data

#### Chart

### National: Spectrum